Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-15 paper.tex
Started section 1

%% Glossary
\newacronym{asd}{ASD}{Autism Spectrum Disorder}

@@

\begin{abstract}
Individuals affected by Autism Spectrum Disorder(ASD) are often unable to communicate in an
appropriate way, they show strong difficulties in social interactions and in manifesting their affective
states.
The conventional techniques, used to improve the performances of these people in the
everyday tasks, are observation-based and can require a lot of effort in terms of time and money, with limited
results.
Technology-assisted teraphies can result more powerful and fast.

Our aim is to analyze the current technology-based solutions that can help therapists in the treatment
of people affected by ASD.
These solutions exploit the joint use of human intelligence and artificial intelligence to improve
the powerfulness of therapies and to allow a better integration of these individuals in the society.
Examples of these type of aids are Virtual Assistants and Agents as therapeutic tools,
wearable technologies or VR headset to help them in everyday communication and to improve their
fundamental and social skills.
An interesting field that can be analyzed is the use of robotic avatar instead of a therapist, in order to increase
the usefulness of a therapy, improving the response and the interaction time of the disabled user.
\end{abstract}

@@

% TODO Brief presentation of ASD (?)
\gls{asd} is a term used to cover a very big set of disorders. In this field there are a lot of studies and experiments, but still is one of the most unknown \DP{forse unknown non è il massimo come termine qui} disease. The symptoms are well known, while the causes are mostly unknown. Nowadays, \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered on a patient at least 3 years old. For this reason, several techniques have been studied to wonder if a children has this disorder in the first 2 years of life.
% TODO Main technologies available until now

\section{Technical Approach}
\label{sec:tech_approach}

\subsection{Simulated Annealing}

>>>>

%% Glossary
\newacronym{asd}{ASD}{Autism Spectrum Disorder}
\newacronym{va}{VA}{Virtual Agents}

@@

\begin{abstract}
Individuals affected by Autism Spectrum Disorder(ASD), especially the not-verbal ones, are often unable to communicate in an
appropriate way, they show strong difficulties in social interactions and in manifesting their affective
states or their necessities.
The conventional techniques, used to improve the performances of these people in the
everyday tasks, are observation-based and can require a lot of effort in terms of time and money, with limited
results.
Technology-assisted therapies can result more powerful and fast.

Our aim is to analyze the current technology-based solutions that can help the therapist and the family of an autistic subject to interact with him.
These solutions exploit the joint use of human intelligence and artificial intelligence to improve
the powerfulness of therapies and to allow a better integration of these individuals in the society.
\end{abstract}

@@

% TODO Brief presentation of ASD (?)
\gls{asd} is a term used to cover a very big set of disorders. In this field there are a lot of studies and experiments, but still is one of the most unknown \DP{forse unknown non è il massimo come termine qui} disease. The symptoms are well known, while the causes are mostly unknown. Nowadays, \textit{screening tests} are used to classify a person as affected by \gls{asd}, but these tests have an high percentage of error (false positive or negative) and they can be administered on a patient at least 3 years old. For this reason, several techniques have been studied to wonder if a children has this disorder in the first 2 years of life.

In this respect, this work is divided in two main sections. In \autoref{sec:thera_tech} we present some innovative tool to improve social skills of a child affected by ASD faster than a classical face-to-face therapy will does \DP{Questa frase fa schifo}.
In \autoref{sec:every_tech} we present a couple of wearable products that allow a faster and easier integration of the subject in the everydays tasks.

\section{Therapeutical techniques}
\label{sec:thera_tech}

The classical way to conduct a therapy session, is a face-to-face meeting between the subject and the therapist.
Usually, is conducted in four phases: the first one is called \textit{Instruction}, in which the therapist explain what is the skill that the subject is going to learn; the second one is the \textit{Modeling} phase, in which the therapist show the patient what he has to do; there is then the \textit{Rehearsal} phase, in which the patient tries to imitate the therapist and finally a \textit{Feedback} phase in which the therapist draw its own conclusions about the test.
The problem of this kind of therapy are the completely subjective evaluation procedure carried out by the therapist and that the subject's attention is not immediate.

%TODO Avatar-based techniques to improve the performances of the therapy
%TODO Methods to detect the anxiety level
To improve the performances of the sessions, the use of \gls{va} has been introducted.

\section{Everydays tools techniques}
\label{sec:every_tech}
